Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Yulia Tsvetkov$^\ast$\ Naama Twitto$^\dagger$\ Nathan Schneider$^\ast$\ Noam Ordan$^\dagger$\\ Manaal Faruqui$^\ast$\ Victor Chahuneau$^\ast$\ Shuly Wintner$^\dagger$ \ Chris Dyer$^\ast$}\\[-3em]

### 2013-04-09 paper/paper.tex
author list

\title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em]
{\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Victor Chahuneau$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]
}

>>>>

\title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] 
{\large Yulia Tsvetkov$^\ast$\ Naama Twitto$^\dagger$\  Nathan Schneider$^\ast$\ Noam Ordan$^\dagger$\\ 
Manaal Faruqui$^\ast$\  Victor Chahuneau$^\ast$\  Shuly Wintner$^\dagger$ \  Chris Dyer$^\ast$}\\[-3em]
}
